\Large \bf One-Step, Three-Factor Authentication With Custom-Fit, In-Ear EEG

### 2017-02-16 paper.tex
missed a space

This study was conducted with a small, relatively homogeneous sample of participants. We feel that more participants from a more diverse pool would greatly improve our understanding and interpretation of the capabilities of this technology. This does not lessen the importance of this work however, as this sample size is comparable to that of previous scalp-based EEG passthoughts work\cite{Ashby2011, Marcel2007a, Palaniappan2008, palaniappan2006electroencephalogram, Poulos2002, Chuang2013b}, the only other in-ear EEG passthoughts study we are aware of \cite{curranpassthoughts} (notably a generic fit system was used here), and other custom-fit in-ear EEG research \cite{kidmose2013study}. The fitting and manufacturing of custom-fit earpieces was the main limitation to increasing our sample size, and may very well pose a limitation in adoption of such a technology. Recently, however there have been developments in at-home kits for creating one's own custom-fitted earpieces \cite{voix2015settable} that could help overcome this barrier in the future.

>>>>

This study was conducted with a small, relatively homogeneous sample of participants. We feel that more participants from a more diverse pool would greatly improve our understanding and interpretation of the capabilities of this technology. This does not lessen the importance of this work however, as this sample size is comparable to that of previous scalp-based EEG passthoughts work \cite{Ashby2011, Marcel2007a, Palaniappan2008, palaniappan2006electroencephalogram, Poulos2002, Chuang2013b}, the only other in-ear EEG passthoughts study we are aware of \cite{curranpassthoughts} (notably a generic fit system was used here), and other custom-fit in-ear EEG research \cite{kidmose2013study}. The fitting and manufacturing of custom-fit earpieces was the main limitation to increasing our sample size, and may very well pose a limitation in adoption of such a technology. Recently, however there have been developments in at-home kits for creating one's own custom-fitted earpieces \cite{voix2015settable} that could help overcome this barrier in the future.
